Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-08 bbbq_article.tex
Use bbbq_1_smart figures

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{../bbbq_1_smart/fig_f_tmh_mhc1_grid.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    See table \ref{tab:tmh_binders_mhc1} for the TMH and epitope counts.
    \richel{Epitope prediction by EpitopePrediction.}.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{../bbbq_1_smart/fig_f_tmh_mhc2_grid.png}
  \caption{
    Percentage of MHC-II epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    \richel{Epitope prediction by NetMHCIIpan.}
    See table \ref{tab:tmh_binders_mhc2} for the TMH and epitope counts.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:2}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../bbbq_1_smart/fig_f_tmh_mhc1_normalized.png}
  \caption{
    Normalized proportion of MHC-I epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc1_normalized}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../bbbq_1_smart/fig_f_tmh_mhc2_normalized.png}
  \caption{
    Normalized proportion of MHC-II epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc2_normalized}
\end{figure}

>>>>

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{../bbbq_1_smart/fig_f_tmh_mhc1_2_grid.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    See table \ref{tab:tmh_binders_mhc1} for the TMH and epitope counts.
    \richel{Epitope prediction by EpitopePrediction.}.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{../bbbq_1_smart/fig_f_tmh_mhc2_2_grid.png}
  \caption{
    Percentage of MHC-II epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    \richel{Epitope prediction by NetMHCIIpan.}
    See table \ref{tab:tmh_binders_mhc2} for the TMH and epitope counts.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:2}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../bbbq_1_smart/fig_f_tmh_mhc1_2_normalized.png}
  \caption{
    Normalized proportion of MHC-I epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc1_normalized}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../bbbq_1_smart/fig_f_tmh_mhc2_2_normalized.png}
  \caption{
    Normalized proportion of MHC-II epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc2_normalized}
\end{figure}
